Plant Modeling for an Autonomous Vehicle

### 2022-04-07 poster.tex
Poster Updates
I edited the vehicle subsystem models and added to the Neural Network and Transfer Function Modeling sections

%\vskip -1cm
$\bullet$ Conducted a literature review to look for existing solutions
$\bullet$ System Architecture 
\begin{figure}
	\centering
	\begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=0.75 cm]
    \tikzstyle{sum} = [draw, circle,fill=orange!15]
    % place nodes
    \node[sum](sum){$\sum$};
    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};

@@

\begin{figure}
	\centering
	 \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
    % Connections
    \draw[stealth-,thick]
    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-2.0,0);
    \draw[-stealth,thick]
    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(2.0,0);
  \end{tikzpicture}
    \caption{Acceleration subsystem block diagram}
    \label{fig:accelModelArchitecture}
\end{figure}

\begin{figure}
	\centering
	  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2.0 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};

    % Connections
    \draw[stealth-,thick]
    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-1.7,0);
    \draw[stealth-,thick]
    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-1.7,0);
    \draw[stealth-,thick]
    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-1.7,0);
    \draw[-stealth,thick]
    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(1.7,0);
    \draw[-stealth,thick]
    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(1.7,0);

@@

\begin{figure}
    \centering
        \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-1.9,0);
    \draw[-stealth,thick]
    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(1.9,0);

@@

\begin{figure}
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1 cm, minimum height=2 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-1.9,0);
    \draw[stealth-,thick]
    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-1.9,0);
    \draw[stealth-,thick]
    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-1.9,0);
    \draw[-stealth,thick]
    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(1.9,0);

@@

\begin{figure}
    \centering
\begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=1.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};

    % Connections
    \draw[stealth-,thick]
    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-1.9,0);
    \draw[-stealth,thick]
    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(1.9,0);

@@

$\bullet$ Data Collection Setup 
\begin{itemize}
	\item Lexus RX450H vehicle platform
	\item Laptop
	\item PACMod ECU 
	\item CANCase
	\item CAN Bus 
\end{itemize}

@@

\begin{block}{Transfer Function Modeling}
\vskip -1cm
%\begin{itemize}
%    \item Determines optimal control gain for dynamic systems
%%    \begin{subequations}
%%        \small
%%        \begin{align}
%%            & \dot{x} = Ax + Bu\\
%%            & u = -Kx\\
%%            & J(u) = \int_{0}^{\infty} (x^TQx + u^TRu + 2x^TNu)dt\\
%%            & A^TS+SA-(SB+N)R^{-1}(B^TS+N^T)+Q=0\\
%%            & K=R^{-1}(B^TS+N^T)
%%        \end{align}
%%    \label{eq:LQR_EQ}
%%    \end{subequations}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[height=.15\textheight,width=.92\textwidth,keepaspectratio=true]{figs/ipe/algorithmFramework}}
    \caption{A desired orientation is given by a user.  The difference between this input and the actual position is calculated.  The controller the calculates the proper amount of voltage to apply to the DC motors.}
    \label{fig:algorithmFramework}
\end{figure}
%\end{itemize} 
\vskip -1cm
\begin{enumerate}
    \item Employ state-space representation of 2-DOF helicopter:
    \begin{align*}
        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
    \end{align*}
    \item Use state feedback law
    \begin{center}
        \vskip -1cm
        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
    \end{center}
    \vskip -1cm
    to minimize the quadratic cost function:
    \begin{align*}
        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
    \end{align*}
    \item Find the solution $\mathbf{S}$ to the Riccati equation
    \begin{align*}
        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
    \end{align*}    
    \item Calculate gain, $\mathbf{K}$
    \begin{center}
        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
    \end{center}
\end{enumerate}

@@

\begin{block}{Neural Network Modeling}
\vskip -1cm
\begin{itemize}
    \item Utilizes gain calculated in LQR
    \item Added Kalman filter to reduce external disturbances to the system
%    \begin{subequations}
%        \small
%        \begin{align}
%            & some eq = x\\
%            & some eq = y\\
%            & some eq = z
%        \end{align}
%    \label{eq:LQG_EQ}
%    \end{subequations}
\end{itemize} 
%\todo[inline]{Insert Dr. Miah's LQG image from his slides here}
\begin{figure}
    \centering
    % \missingfigure{Insert figure.}
    % \fcolorbox{gray!10}{gray!10}{\includegraphics[width=1.05\textwidth,keepaspectratio=true]{figs/img/LQG_SimulinkResize.png}}
    \caption{Noise resistant 2-DOF helicopter model.}
    \label{fig:LQGModel}
\end{figure}

>>>>

%\vskip -1cm
$\bullet$ Conducted a literature review to look for existing solutions
$\bullet$ System Architecture 
\begin{figure}
	\centering
	\begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=0.75 cm]
    \tikzstyle{sum} = [draw, circle,fill=orange!15]
    % place nodes
    \node[sum](sum){$\sum$};
    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};

@@

\begin{figure}
	\centering
	 \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width= 5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
    % Connections
    \draw[stealth-,thick]
    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-5.0,0);
    \draw[-stealth,thick]
    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(5.0,0);
  \end{tikzpicture}
    \caption{Acceleration subsystem block diagram}
    \label{fig:accelModelArchitecture}
\end{figure}

\begin{figure}
	\centering
	  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2.0 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};

    % Connections
    \draw[stealth-,thick]
    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-4.5,0);
    \draw[stealth-,thick]
    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-4.5,0);
    \draw[stealth-,thick]
    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-4.5,0);
    \draw[-stealth,thick]
    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(4.5,0);
    \draw[-stealth,thick]
    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(4.5,0);

@@

\begin{figure}
    \centering
        \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
    \draw[-stealth,thick]
    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);

@@

\begin{figure}
    \centering
  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};

    % Connections
    \draw[stealth-,thick]
    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
    \draw[stealth-,thick]
    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
    \draw[stealth-,thick]
    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
    \draw[-stealth,thick]
    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);

@@

\begin{figure}
    \centering
\begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};

    % Connections
    \draw[stealth-,thick]
    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
    \draw[-stealth,thick]
    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);

@@

%$\bullet$ Data Collection Setup 
\begin{itemize}
	\item Data Collection Setup
		\item Lexus RX450H vehicle platform
	\item Laptop
	\item PACMod ECU 
	\item CANCase
	\item CAN Bus 
\end{itemize}

@@

\begin{block}{Transfer Function Modeling}
\vskip -1cm
\begin{itemize}
    \item MATLAB's System Identification Toolbox used to create models 
    \item Models needed to meet best fit and error requirements

\end{itemize} 
\vskip -1cm
%\begin{enumerate}
%    \item Employ state-space representation of 2-DOF helicopter:
%    \begin{align*}
%        \dot{\mathbf{x}} = \mathbf{A}\mathbf{x} + \mathbf{B}\mathbf{u}
%    \end{align*}
%    \item Use state feedback law
%    \begin{center}
%        \vskip -1cm
%        $\mathbf{u} = -\mathbf{K}\mathbf{x}$
%    \end{center}
%    \vskip -1cm
%    to minimize the quadratic cost function:
%    \begin{align*}
%        J(\mathbf{u}) = \int_0^\infty (\mathbf{x}^T\mathbf{Q}\mathbf{x} + \mathbf{u}^T\mathbf{R}\mathbf{u} + 2\mathbf{x}^T\mathbf{N}\mathbf{u})\mathrm{dt}
%    \end{align*}
%    \item Find the solution $\mathbf{S}$ to the Riccati equation
%    \begin{align*}
%        \mathbf{A}^T\mathbf{S}+\mathbf{SA}-(\mathbf{SB}+\mathbf{N})\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)+\mathbf{Q}=0
%    \end{align*}    
%    \item Calculate gain, $\mathbf{K}$
%    \begin{center}
%        $\mathbf{K}=\mathbf{R}^{-1}(\mathbf{B}^T\mathbf{S}+\mathbf{N}^T)$
%    \end{center}
%\end{enumerate}

@@

\begin{block}{Neural Network Modeling}
\vskip -1cm
\begin{itemize}
    \item Used MATLAB's Neural Network Time Series App
    \item Generated models using the Bayesian Regularization Algorithm
    \item Models trained using collected log data  
\end{itemize}

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
	\caption{Steering System Training Plots}
    \label{fig:SteeringSysNeuralNetwork}
\end{figure}

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
	\caption{Acceleration System Training Plots}
    \label{fig:AccelerationSysNeuralNetwork}
\end{figure}

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
	\caption{Brake System Training Plots}
    \label{fig:BrakeSysNeuralNetwork}
\end{figure}
